### 2019-11-06 report/paper.tex
add hog / hov implementation

\end{abstract}
%%%% body goes in here %%%%
\section{Introduction}
"Where's Waldo" is a series of books containing detailed, high-resolution illustrations. For this project, we are given a set of scanned images from the book, and are tasked to design a computer vision algorithm that can detect the three characters from the book: Waldo, Wenda, and the Wizard. Each image may contain one or more of these characters. We are provided with a set of training images with annotations of the bounding box locations of Waldo, Wenda, or the Wizard in each image.\\

@@

@@

\section{Experiments}
\subsection{Data Preparation and Configuration}

@@

\begin{table}[]
    \centering
    \begin{tabular}{ccc}
        \toprule
        Class name & \#samples & percentage \\
        \midrule
        waldo & 137 &  1.01\% \\
        wenda & 43&  0.32\% \\
        wizard& 27&  0.20\% \\
        negative & 13315&  98.47\% \\
        \bottomrule
    \end{tabular}
    \label{tab:dataset-stats}
    \caption{Dataset statistics for the training}
\end{table}

% Specify how to process the data, how to evaluate the performance (e.g., mAP).
% \begin{table}[ht]
%     \centering
%     \begin{tabular}{l|c|c|c}
%     \hline
%      Dataset & \#train & \#test & \#Category\\
%     \hline
%     MNIST& 60,000 & 10,000 & 10  \\
%     CIFAR-10& 50,000 & 10,000 & 10 \\
%     \hline
%     \end{tabular}
%     \caption{Summary of datasets.}
%     \label{tab:dataset}
% \end{table}

\subsection{Implementation}\label{sec:implemenation}
Give a figure to illustrate your implementation, then detail each parts.

\subsection{Results}
Present the results, both qualitatively (visualize) and quantitatively (specific numbers)..
Analyze the results
\subsection{Discussion}
Strengths and weakness in your method.

@@

\section{Group Information}
\begin{table*}[ht]
    \centering
    \begin{tabular}{l|c|c|c}
    \hline
     Member & Student ID & Email & Contribution\\
    \hline
    Maximilian Fruehauf& Axx & e0445541@u.nus.edu & xxx \\
    David Drews& Axx &e0454245@u.nus.edu & xxx  \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & xxx  \\
    \hline
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}
\bibliographystyle{plain}

>>>>

\end{abstract}
%%%% body goes in here %%%%
\section{Introduction}

"Where's Waldo" is a series of books containing detailed, high-resolution illustrations. For this project, we are given a set of scanned images from the book, and are tasked to design a computer vision algorithm that can detect the three characters from the book: Waldo, Wenda, and the Wizard. Each image may contain one or more of these characters. We are provided with a set of training images with annotations of the bounding box locations of Waldo, Wenda, or the Wizard in each image.\\

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/waldo_winter} 
    \caption{Exmaple of an image showing detections with \( (name, p, p_{ratio}) \) in red, ground truth in green}
    \label{fig:waldo-winter}
\end{figure}

@@

\section{Experiments}
\subsection{Data Preparation and Configuration}\label{subsec:data-prep}

@@

\begin{table}[]
    \centering
    \begin{tabular}{ccc}
        \toprule
        Class name & \#samples & percentage \\
        \midrule
        waldo & 137 &  1.01\% \\
        wenda & 43&  0.32\% \\
        wizard& 27&  0.20\% \\
        negative & 13315&  98.47\% \\
        \bottomrule
    \end{tabular}
    \caption{Dataset statistics for the training}
    \label{tab:dataset-stats}
\end{table}

\subsection{Implementation}\label{sec:implemenation}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/model_overview} 
    \caption{Schematic overview of the wlado / wenda / wizard detection pileline.}
    \label{fig:model-overview}
\end{figure}

The pipeline for detecting the classes of a given bounding box are displayed in \autoref{fig:model-overview},
the first 3 steps of which are covered in \autoref{subsec:data-prep}. In the following paragraps we will focus on the
steps 4-7 of any detection and provide some details of interest in the implementation.

\paragraph{HOG \& HOV feauture descritor}
To capture shape and color information from the preprocessed sample images, we adopt a twofold feature descriptor, 
which consists of the HOG descriptor and a histogramed version of the SIFT detector, we call HOV.

HOG works by first calculating the horizontal and vertical gradients in the image, which are then separated into
quadratic cells. From both a horizontal and vertical window, the magnitude and direction (radians or degrees) of the gradient get computed.
Then the magnitude is binned according to the corresponding direction. These bins then form a histogram for the cell.
This gives some invariance of the feature descriptor to slight pixel value changes. 
To also gives some spatial invariance, a set number of these histogramed cells are concatenated together. Which is repeated for each cell.
In a final step, the resulting feature vector is normalized with one of a multitude of possible norms. We decided to use the \( L_2 \)-Hys norm.

The HOV (Histograms over Values) descriptor works essentially the same (in fact most of the code is copied from the \verb|scikit-learn| HOG implemenation),
with the only difference being that the initial histogram on each cell is not computed from the gradient of the input,
but rather the values of the input image inself.

Concatenating these two independently (with the same parameters) computed feature descriptors gives a good spatial and
value representation of the input images. The effect of which we evaluate in \autoref{subsec:results}.

\paragraph{SVM Classification}

\paragraph{Non-Maximum suppression}

\paragraph{Class Label outputs}

\subsection{Results}\label{subsec:results}
Present the results, both qualitatively (visualize) and quantitatively (specific numbers)..
Analyze the results

Evaluate hog only vs hog / hov
\subsection{Discussion}
Strengths and weakness in your method.

@@

\section{Group Information}
\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    % \hline
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& Axx & e0445541@u.nus.edu & xxx \\
    David Drews& Axx &e0454245@u.nus.edu & xxx  \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & xxx  \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}
\bibliographystyle{plain}
